An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
a couple edits to data collection section

Another motivation was a desire to collect data on students' work
on programming exercises as a way to study how students learn to program.
For example, CloudCoder captures a fine-grained edit history of each
student's work on each exercise.  Because the system is open source,
we (and other researchers) can easily add other kinds of data collection
to the system.

@@

CloudCoder logs keystrokes in the online editor window, and 
stores all submissions and test outcomes in a databases.
We hope that the combination of exercises and data will give faculty
insights into the difficulty level of different exercises, keep a
record of common error patterns, and enable the development of
innovative data analyses.

One question is how to manage the data collected.  
Recent work on web-scale data collection by the BlueJ team
\cite{Utting:2012:WDG:2361276.2361278} lays out a number of important
questions about programming data, such as who should have access to the data, and what
mechanism should be used to access the data.  Sanders
et. al.\cite{Sanders:2008:DSE:1404520.1404534} reviewed a number of
the challenges involved in sharing empirical education data.

>>>>

Another motivation was a desire to collect data on students' work
on programming exercises as a way to study how students learn to program.
For example, CloudCoder captures a fine-grained edit history of each
student's work on each exercise.  Because the system is open source,
we (and other researchers) can easily add support for other kinds of data collection.

@@

As the student works on an exercises, CloudCoder logs all of the
student's edits, and stores all submissions and test outcomes.
We hope that the combination of exercises and data will give faculty
and researchers
insights into the difficulty level of different exercises, keep a
record of common error patterns, and enable the development of
innovative data analyses.

One question is how to manage the data collected.  
Recent work on web-scale data collection by the
BlueJ team\cite{Utting:2012:WDG:2361276.2361278} lays out a number of important
questions about programming data, such as who should have access to the data, and what
mechanism should be used to access the data.  Sanders
et.\ al.\cite{Sanders:2008:DSE:1404520.1404534} reviewed a number of
the challenges involved in sharing empirical education data.
